Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-04 manu-draft.qmd
copying data and R funcs from hmpu-workflow, scoping out tables/figs
added gis workflow figure

filters: 
  - templates/scholarly-metadata.lua
  - templates/author-info-blocks.lua
---

@@

@@

>>>>

filters: 
  - templates/scholarly-metadata.lua
  - templates/author-info-blocks.lua

execute: 
  echo: false
  warning: false
---

```{r, results = 'hide'}
library(knitr)
library(here)
```

@@

Figure \@ref(fig:gisworkflow).

@@

## Figures

```{r gisworkflow}
#| fig.cap: 'Spatial analysis workflow used to identify opportunity areas for habitat conservation and restoration in the Tampa Bay watershed.  Workflows are divided into binning of land use/land cover categories into relevant habitat types and spatial overlay of datasets to identify the opportunity areas.'
knitr::include_graphics(here('figs/gisworkflow.png'))
```

Figure 2: Land use change as Sankey

Figure 3: Subtidal habitat change as Sankey

Figure 4: Map of opportunity assessment

Figure 5: Map of restoration potential

## Tables

Table 1: Land use change table

Table 2: Subtidal change table

Table 3: Summary of the opportunity assessment analysis

Table 4: Targets
